Merging Datasets Through Deep learning

### 2018-09-04 paper2018/evaluation.tex
wording

\begin{table}[ht]
\caption{Precision and Recall by loss functions}
\label{precision_recall}
\begin{center}
%{\scriptsize
\begin{tabular}{|l|l|r|r|r|}
\hline
Entities & Loss & Recall & \multicolumn{2}{|c|}{Precision} \\
 & & & @1 & All \\
\hline
\multirow{4}{*}{People} & Adapted & .81 & .81 & .63 \\
\cline{2-5}
& Triplet & .74 & .84 & .55 \\
\cline{2-5}
& Improved & .71 & .52 & .45 \\
\cline{2-5}
& Angular & .04 & .09 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & .72 & .73 & .64 \\
\cline{2-5}
& Triplet & .75 & .76 & .67 \\
\cline{2-5}
& Improved & .74 & .72 & .64 \\
\cline{2-5}
& Angular & .26 & .32 & .22 \\
\hline
\end{tabular} %}
\end{center}
\end{table}

\begin{table}[ht]
\caption{Distance estimates after training}
\label{distance}
\begin{center}
%{\scriptsize 
\begin{tabular}{|l|l|r|r|r|r|}
\hline
Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c|}{Neg} \\
& & Mean & Std & Mean & Std \\
\hline
\multirow{4}{*}{People} & Adapted & 1.59 & 4.04 & 2.44 & 2.45 \\
\cline{2-6}
& Triplet & .46 & .18 & .55 & .10 \\
\cline{2-6}
& Improved & .15 & .38 & .21 & .18 \\
\cline{2-6}
& Angular & .51 & .25 & .06 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & 2.38 & 3.77 & 3.23 & 1.71 \\
\cline{2-6}
& Triplet & .39 & .28 & .55 & .09 \\
\cline{2-6}
& Improved & .32 & .50 & .42 & .19 \\
\cline{2-6}
& Angular & .07 & .04 & .04 & .01 \\
\hline
\end{tabular}%}
\end{center}
\end{table}

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  To quantify recall, we measured, for each loss function.  The numbers for our adapted loss function were 81\% for people and 72\% for companies, so a join could capture most similar names.  Furthermore, the adapted loss function showed better performance on the harder people dataset, but there was a small advantage for the triplet loss function in the easier company data, see Table \ref{precision_recall}.  Furthermore, it appears that triplet loss and its variants are better than angular loss for learning this problem.

>>>>

\begin{table}[ht]
\caption{Precision and Recall by loss functions}
\label{precision_recall}
\begin{center}
%{\scriptsize
\begin{tabular}{|l|l|r|r|r|}
\hline
Entities & Loss & Recall & \multicolumn{2}{|c|}{Precision} \\
 & & & @1 & All \\
\hline
\multirow{4}{*}{People} & Adapted & .81 & .81 & .63 \\
\cline{2-5}
& Triplet & .74 & .84 & .55 \\
\cline{2-5}
& Improved & .71 & .52 & .45 \\
\cline{2-5}
& Angular & .04 & .09 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & .74 & .73 & .66 \\
\cline{2-5}
& Triplet & .74 & .75 & .67 \\
\cline{2-5}
& Improved & .74 & .72 & .65 \\
\cline{2-5}
& Angular & .26 & .32 & .22 \\
\hline
\end{tabular} %}
\end{center}
\end{table}

\begin{table}[ht]
\caption{Distance estimates after training}
\label{distance}
\begin{center}
%{\scriptsize 
\begin{tabular}{|l|l|r|r|r|r|}
\hline
Entities & Loss & \multicolumn{2}{|c|}{Pos} & \multicolumn{2}{|c|}{Neg} \\
& & Mean & Std & Mean & Std \\
\hline
\multirow{4}{*}{People} & Adapted & 1.59 & 4.05 & 2.44 & 2.45 \\
\cline{2-6}
& Triplet & .46 & .18 & .55 & .10 \\
\cline{2-6}
& Improved & .15 & .38 & .21 & .18 \\
\cline{2-6}
& Angular & .51 & .25 & .06 & .02 \\
\hline
\multirow{4}{*}{Corps} & Adapted & 2.39 & 3.62 & 3.59 & 2.72 \\
\cline{2-6}
& Triplet & .43 & .31 & .59 & .09 \\
\cline{2-6}
& Improved & .32 & .50 & .42 & .19 \\
\cline{2-6}
& Angular & .07 & .04 & .04 & .01 \\
\hline
\end{tabular}%}
\end{center}
\end{table}

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  The numbers for our adapted loss function were 81\% for people and 72\% for companies, so a join could capture most similar names.  For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).  Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.  On the other hand, for companies the only significant difference was that angular was worse.
